### 2016-09-30 architecture.tex
Better wording

The \texttt{Function} class is a subclass of \texttt{Expr} which makes it
easier to define mathematical functions called with arguments. This includes
named functions like $\sin(x)$ and $\log(x)$ as well as undefined functions
like $f(x)$. Subclasses of \texttt{Function} should define a
class method \texttt{eval}, which returns a canonical form of the function
application (usually an instance of some other class, i.e., a \texttt{Number})
or \texttt{None}, if for given arguments that function should not be
automatically evaluated.

>>>>

The \texttt{Function} class is a subclass of \texttt{Expr} which makes it
easier to define mathematical functions called with arguments. This includes
named functions like $\sin(x)$ and $\log(x)$ as well as undefined functions
like $f(x)$. Subclasses of \texttt{Function} should define a
class method \texttt{eval}, which returns an evaluated value for the function
application (usually an instance of some other class, i.e., a \texttt{Number}),
or \texttt{None} if for given arguments that function should not be
automatically evaluated.
